Pangenome graph layout by HOGWILD! path-guided stochastic gradient descent

### 2022-09-21 manuscript/main.tex
update affiliations

\author{ %[Heumos, \textit{et~al}.]{
  Simon Heumos\,$^{1,2 \dagger}$,
  Andrea Guarracino\,$^{3 \dagger}$,
  Jan-Niklas Manuel Schmelzle\,$^{4,5}$,
  Jiajie Li\,$^{4,5}$,
  Sven Nahnsen\,$^{1,2}$,
  Pjotr Prins\,$^6$,
  and Erik Garrison\,$^{6 *}$
}

@@

\section*{Funding}
S.H. acknowledges funding from the Central Innovation Programme (ZIM) for SMEs of the Federal Ministry for Economic Affairs and Energy of Germany. S.N. acknowledges Germany’s Excellence Strategy (CMFI), EXC-2124 and (iFIT)—EXC 2180–390900677. This work was supported by the BMBF-funded de. NBI Cloud within the German Network for Bioinformatics Infrastructure (de.NBI) [031A537B, 031A533A, 031A538A, 031A533B, 031A535A, 031A537C, 031A534A and 031A532B].

>>>>

\author{ %[Heumos, \textit{et~al}.]{
  Simon Heumos\,$^{1,2 \dagger}$,
  Andrea Guarracino\,$^{3 \dagger}$,
  Jan-Niklas Manuel Schmelzle\,$^{4,5}$,
  Jiajie Li\,$^{4,5}$,
  Zhiru Zhang\,$^{5}$,
  Sven Nahnsen\,$^{1,2}$,
  Pjotr Prins\,$^6$,
  and Erik Garrison\,$^{6 *}$
}

@@

\section*{Funding}
JNM.S., J.L., and Z.Z. acknowledge funding from the NSF PPoSS Award \#2118709.
S.H. acknowledges funding from the Central Innovation Programme (ZIM) for SMEs of the Federal Ministry for Economic Affairs and Energy of Germany. S.N. acknowledges Germany’s Excellence Strategy (CMFI), EXC-2124 and (iFIT)—EXC 2180–390900677. This work was supported by the BMBF-funded de. NBI Cloud within the German Network for Bioinformatics Infrastructure (de.NBI) [031A537B, 031A533A, 031A538A, 031A533B, 031A535A, 031A537C, 031A534A and 031A532B].
